\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[chorded]{songs}
\noversenumbers
\begin{document}

\songsection{Worship Songs}

\begin{songs}{}
\beginsong{To our God}[by={Bethel Music},
sr={},
cr={}]
\transpose{0}
\beginverse\memorize
\[Em]Up from the \[C]ashes,
Your love has \[G]brought us
Out of the \[D]darkness,
into the \[Em]light.
Lifting our \[C]sorrows,
bearing our \[G]burdens
Healing our \[D]hearts.
\endverse

\beginverse
\[Em]To our God, we lift up one \[C]voice
To our God, we lift up one \[G]song
To our God, we lift up one \[D]voice
Hallelu\[Em]jah
Hallelu\[D]jah
Hallelu\[G]jah
Hallelu\[D]jah
Hallelu\[Em]jah
\endverse

\beginverse
^Chains have been ^broken,
eyes have been ^opened
An army of ^dry bones
is starting to ^rise
Death is de^feated,
we are vic^torious
For You are a^live
\endverse

\beginverse
We'll make His \[Em]praise
\[C]glorious, \[G]glorious, \[D]glorious
For His \[Em]name is
\[C]glorious, \[G]glorious, \[D]glorious
Make His \[Em]praise
\[C]glorious, \[G]glorious, \[D]glorious
Shout His \[Em]name
\[C]glorious, \[G]glorious, \[D]glorious
\endverse
\endsong




\beginsong{Come Awaken Love}[by={Bethel Music},
sr={},
cr={}]
\transpose{0}
\beginverse
Verse:
\[A]Like a \[E/G#]fire in the \[B]night,
Who's flames \[C#m]reach
And touch the \[A]sky
Burn with\[E/G#]in my soul and \[B]mind,
`Till all I \[C#m]see are Your \[A]eyes
Like the \[E/G#]dawn takes back the \[B]light,
Like Your \[C#m]Son brought back to \[A]life
Resur\[E/G#]rect my soul's de\[B]sire
 To burn \[C#m]again
With true love's \[F#m]\[C#m]\[B]fire
With true love's \[F#m]\[C#m]\[B]fire
\endverse

\beginverse
Chorus:
Lord God \[C#m]come a\[A]waken \[E]love
Come stir my soul to \[C#m]long
for \[A]all You \[E]are
I'm desperate just to \[C#m]have
more \[A]of Your \[E]heart
Come awaken \[C#m]\[A]\[E]love

Verse
Chorus
\endverse


\beginverse
Bridge:
Cause \[A]I live to \[E]love You
Al\[C#m]mighty God of \[B]love
And my de\[A]sire is to \[E]know you
And \[C#m]give you all my \[B]heart
Chorus 2x
\endverse

\endsong



\beginsong{Holy and anointed One}[by={John Barnett},
sr={},
cr={}]
\transpose{0}
\beginverse
{\[G]\[D]Je}\[C]sus,   {\[G]\[D]Je}\[C]sus, 
\[G]Holy\[D]and A\[Am7]nointed \[C]One, 
{\[G]\[D]Je}\[G]sus 
 
{\[G]\[D]Je}\[C]sus,   {\[G]\[D]Je}\[C]sus, 
\[G]Risen \[D]and Ex\[Am7]alted \[C]One, 
{\[G]\[D]Je}\[G]sus 
\endverse

\beginverse
Your name is like \[C]honey on my \[G]lips, 
You Spirit like \[C]water to my \[G]soul, 
Your word is a \[C]lamp unto my \[Em7]feet, 
Jesus I \[C]love You, I \[D]love You
\endverse
\endsong



\beginsong{No Greater Name}[by={Daniel Warkentin},
sr={},
cr={}]
\transpose{0}
\beginverse
There is \[E]no greater \[B]name,
than the \[A]name of \[E]Jesus.
\[A]No greater \[C#m]name that I \[B]know.
There is \[E]no greater \[B]name,
than the \[C#m]name of my \[A]saviour.
No greater \[B]name that I \[E]know.
\endverse

\beginverse
There is \[E]no greater \[B]love,
than the \[A]love of \[E]Jesus.
\[A]No greater \[C#m]love that I \[B]know.
There is \[E]no greater \[B]love,
than the \[C#m]love of my \[A]saviour.
No greater \[B]love that I \[E]know.
\endverse
\endsong




\beginsong{Jesus We Love You}[by={Bethel Music},
sr={},
cr={}]
\transpose{-4}
\beginverse\memorize
Verse 1:
Old things have \[E]passed away
Your love has \[B]stayed the same
Your constant \[E]grace remains the \[B]cornerstone

Things that we \[E]thought were dead
Are breathing in \[B]life again
You cause your \[E]Son to shine on darkest \[B]nights
\endverse

\beginverse
Pre Chorus:
For \[F#]all that you've done 
we will pour \[G#m]out our love
This will \[E]be our anthem \[F#]song
\endverse

\beginverse
Chorus:
Jesus we \[E]love you
Oh how we \[B]love you
You are the \[E]one our hearts \[B]adore
\endverse

\beginverse
Verse 2:
The hopeless have ^found their hope
The orphans now ^have a home
All that was ^lost has
found its place in ^you

You lift our ^weary head
You make us ^strong instead
You took these ^rags and
made us ^beautiful
\endverse

\beginverse
Bridge:
\[E]Our affection, our devotion 
\[B]poured out on the feet of Jesus
\[E]Our affection, our devotion 
\[B]poured out on the feet of Jesus
\[C#m]Our affection, our devotion 
\[B/D#]poured out on the feet of Jesus
\[E]Our affection, our devotion 
\[F#]poured out on the feet of \[F#]Jesus
\endverse
\endsong



\beginsong{Welch ein Freund ist unser Jesus}[by={Joseph M. Scriven},
sr={},
cr={}]
\transpose{-4}
\beginverse\memorize
\[F]Welch ein Freund ist unser \[B]Jesus,
\[F]O, wie hoch ist er \[C]erhöht!
\[F]Er hat uns mit Gott ver\[B]söhnet
\[F]Und ver\[C]tritt uns im Ge\[F]bet.
\[C]Wer mag sagen und er\[F]messen,
\[B]Wieviel \[F]Heil verloren \[C]geht,
\[F]Wenn wir nicht zu ihm uns \[B]wenden
\[F]Und ihn \[C7]suchen im Ge\[F]bet!
\endverse

\beginverse
Wenn des Feindes Macht uns drohet
Und manch Sturmwind um uns weht,
Brauchen wir uns nicht zu fürchten,
Stehn wir gläubig im Gebet.
Da erweist sich Jesu Treue,
Wie er uns zur Seite steht,
Als ein mächtiger Erretter,
Der erhört ein ernst Gebet.
\endverse

\beginverse
Sind mit Sorgen wir beladen,
Sei es frühe oder spät,
Hilft uns sicher unser Jesus,
Fliehn zu ihm wir im Gebet.
Sind von Freunden wir verlassen
Und wir gehen ins Gebet,
O, so ist uns Jesus alles:
König, Priester und Prophet!
\endverse

\beginverse
Kommen Prüfungen und Leiden,
scheint's, als ob's nicht weitergeht,
wird die Not am allergrößten,
flieg zu Jesus im Gebet.
Jesus bleibt des Herzens Zuflucht,
selig, wer im Glauben fleht.
Er deckt uns mit starken Armen,
schenkt uns Ruhe im Gebet.
\endverse

\beginverse
^What a friend we have in ^Jesus,
^All our sins and griefs to ^bear!
^What a privilege to ^carry
^Ev'ry^thing to God in ^prayer!
^Oh, what peace we often ^forfeit,
^Oh, what needless pain we ^bear,
^All because we do not ^carry
^Ev'ry^thing to God in ^prayer!
\endverse

\beginverse
Have we trials and temptations?
Is there trouble anywhere?
We should never be discouraged,
Take it to the Lord in prayer:
Can we find a friend so faithful
Who will all our sorrows share?
Jesus knows our ev'ry weakness,
Take it to the Lord in prayer.
\endverse

\beginverse
Are we weak and heavy laden,
Cumbered with a load of care?
Precious Savior, still our refuge;
Take it to the Lord in prayer:
Do thy friends despise, forsake thee?
Take it to the Lord in prayer;
In His arms He'll take and shield thee;
Thou wilt find a solace there.
\endverse
\endsong



\beginsong{The One Thing}[by={Paul Colman},
sr={},
cr={}]
\transpose{0}
\beginverse
Verse 1
Well \[F]here I \[C]am
in a \[G]river of \[C]questions 
Can I \[F]pour my \[C]heart out
to a \[G]listening \[C]ear
I \[F]see this \[C]life,
its \[G]valleys and \[C]mountains 
And I \[F]think of all the \[C]roads
that \[G]brought me \[C]here
Oh that \[F]brought me \[C]here\[G]\[C]      
\endverse

\beginverse
Verse 2:
Well I've \[F]questioned my \[C]reasons
this \[G]life I'm \[C]living 
I've \[F]questioned my a\[C]bility
to judge \[G]wrong from \[C]right 
Well I've \[F]questioned all the \[C]things
I've \[G]ever called \[C]certain 
My \[F]race, my re\[C]ligion,
my \[G]country, my \[C]mind 
\endverse

\beginverse
Chorus:
\lrep But the \[F]one thing \[C]I don't
\[G]question is \[C]You  
You really \[F]love \[C]me
like You \[G]say You \[C]do \rrep \rep{2}
You really \[F]love \[C]me
like You \[G]say You \[C]do 
So \[F]hold \[C]me\[G]\[C]
\[F]Hold \[C]me\[G]\[C]
\endverse

\beginverse
Verse 3:
Well I've \[F]questioned sig\[C]nificance,
\[G]meaning and \[C]relevance 
Does the \[F]work I'm \[C]doin'
really \[G]matter at \[C]all? 
Well I've \[F]questioned my \[C]friendship,
al\[G]liance, de\[C]pendence
\[F]Who will \[C]still be here \[G]when I \[C]fall? 
\endverse

\beginverse
Bridge:
  \[F]Only one thing \[C]doesn't change,
  \[G]only one thing \[C]stays the same
  \[F]All I know at the \[C]end of the day is
  \[G]Your love re\[C]mains
  \[F]Only one thing \[C]doesn't change,
  \[G]only one thing \[C]stays the same
  \[F]All I know at the \[C]end of the day is
  \[G]Your love re\[C]mains
\endverse
\endsong




\beginsong{Vater, unser Vater}[by={Text: Christoph Zehnender, Mel.: Hans-Werner Scharnowski},
sr={},
cr={}]
\transpose{0}
\beginverse\memorize
Bist zu \[E]uns wie ein Vater,
der sein \[A]Kind nie ver\[E]gißt.
Der trotz \[E]all seiner \[C#m]Größe
immer \[A]ansprechbar \[E]ist.
Deine \[E]Herrschaft soll kommen.
Das, was \[A]du willst, ge\[E]schehn.
Auf der \[E]Erde, im \[C#m]Himmel
sollen \[A]alle es \[E]sehn.
\endverse

\beginverse
\[E]Vater, unser \[A]Va\[E]ter,
alle \[A]Ehre \[E]deinem \[C#m]Na\[H]men
\[E]Vater, unser \[A]Va\[E]ter,
bis ans \[A]Ende der \[E]Zeiten, \[H]A\[E]men!

\endverse
\chordsoff
\beginverse
Lehre uns zu vergeben,
so wie du uns vergibst.
Laß uns treu zu dir stehen,
so wie du immer liebst.
Gib uns das, was wir brauchen,
gib uns heut unser Brot.
Und vergib uns den Aufstand,
gegen dich und dein Gebot.
\endverse

\beginverse
Nimm Gedanken des Zweifels
und der Anfechtung fort.
Mach uns frei von dem Bösen,
durch dein mächtiges Wort.
Deine Macht hat kein Ende,
wir vertrauen darauf.
Bist ein herrlicher Herrscher
und dein Reich hört nie auf.
\endverse

\chordson
\endsong


\end{songs}
\end{document}